Multiway Spherical Clustering via \\ Degree-Corrected Tensor Block Models

### 2022-01-18 tensor_clustering/tensor_clustering_ieee/ieee_v3.tex
v3

    {\bf Step 3 (Derivation of contraction inequality).} In this step we derive the upper bound of $\zeta_{ib}$ and obtain the contraction inequality~\eqref{eq:proof_5_ineq}. Note that 
    \begin{align}
        \zeta_{ib}^{(t)} &= \theta(i) \onormSize{}{ [ \mS_{ z(i):}  ]^s - [ \mS_{b:}  ]^s  }^2 \ind \offf{z^{(t+1)}(i) = b, \frac{1}{2}\onormSize{}{ [ \mS_{z(i):}  ]^s - [ \mS_{b:}  ]^s  }^2 \leq (\theta(i) m)^{-1} F_{ib}^{(t)} + G_{ib}^{(t)} + H_{ib}^{(t)} }\\
        & \leq \theta(i) \onormSize{}{ [ \mS_{ z(i):}  ]^s - [ \mS_{b:}  ]^s  }^2 \ind \offf{z^{(t+1)}(i) = b, \frac{1}{4}\onormSize{}{ [ \mS_{z(i):}  ]^s - [ \mS_{b:}  ]^s  }^2 \leq (\theta(i) m)^{-1} F_{ib}^{(t)} + G_{ib}^{(t)} } \\
        & \leq 64 \ind \offf{ z^{(t+1)}(i) = b} \of{  \frac{(F_{ib}^{(t)})^2}{ cm^2\onormSize{}{ [ \mS_{z(i):}  ]^s - [ \mS_{b:}  ]^s  }^2} + \frac{\theta(i)(G_{ib}^{(t)})^2}{ \onormSize{}{ [ \mS_{z(i):}  ]^s - [ \mS_{b:}  ]^s  }^2}    }
        %&\leq  \ind \offf{ z^{(t+1)}(i) = b} \of{  \frac{(F_{ib}^{(t)})^2}{ \onormSize{}{ [ \mS_{z(i):}  ]^s - [ \mS_{b:}  ]^s  }^2} + \frac{\theta(i)(G_{ib}^{(t)})^2}{ \onormSize{}{ [ \mS_{z(i):}  ]^s - [ \mS_{b:}  ]^s  }^2}    },\label{eq:zeta}
    \end{align}
    where the first inequality follows from the inequality~\eqref{eq:hib} in Lemma~\ref{lem:upper_fgh}, and the last inequality follows from the assumption that $\min_{i \in [p]} \theta(i) \geq c>0$. Choose the constant $\tilde C$ in the condition SNR $\geq \tilde C p^{-K/2} \log p$ that satisfies inequalities~\eqref{eq:tilde_c1} and \eqref{eq:tilde_c2}. Following \citet[Step 4, Proof of Theorem 2]{han2020exact} and Lemma~\ref{lem:upper_fgh}, we have 
    \begin{align}\label{eq:f_sum}
          \frac{1}{p} \sum_{i \in [p]}\sum_{b \in [r]/z(i)} \ind \offf{ z^{(t+1)}(i) = b} \frac{(F_{ib}^{(t)})^2}{ cm^2 \onormSize{}{ [ \mS_{z(i):}  ]^s - [ \mS_{b:}  ]^s  }^2} \leq \frac{C_0 \bar C}{c m^2 \tilde C^2} L^{(t)},
    \end{align}
   for a positive universal constant $C$ and 
    \begin{align}
         \frac{1}{p} \sum_{i \in [p]}\sum_{b \in [r]/z(i)} \ind \offf{ z^{(t+1)}(i) = b} \frac{\theta(i)(G_{ib}^{(t)})^2}{ \onormSize{}{ [ \mS_{z(i):}  ]^s - [ \mS_{b:}  ]^s  }^2}  &\leq \frac{1}{512} \frac{1}{p} \sum_{i \in [p]}\theta(i) \sum_{b \in [r]/z(i)}   \ind \offf{ z^{(t+1)}(i) = b}  (\Delta_{\min}^2 + L^{(t)}) \\
         & \leq \frac{1}{512} (L^{(t+1)} + L^{(t)}), \label{eq:g_sum}
    \end{align}
    where the last inequality follows from the definition of $L^{(t)}$ and the constraint of $\mtheta$ in parameter space~\eqref{eq:family}. 
    %Choosing the constants $C, \bar C, C_2$ in~\eqref{eq:zeta}~\eqref{eq:f_sum}~\eqref{eq:g_sum} carefully \fixme{Miaoyan}{be specific. Add one sentence to explain}, 
   For $\tilde C$ also satisfies 
    \begin{equation}\label{eq:tilde_c3}
         \frac{C_0 \bar C}{c m^2 \tilde C^2} \leq \frac{1}{512},
    \end{equation}
    we have 
    \begin{equation}\label{eq:zeta_upper}
        \frac{1}{p}\sum_{i \in [p] }  \sum_{b \in [r]/z(i)}  \zeta_{ib}^{(t)} \leq  \frac{1}{8} L^{(t+1)}  + \frac{1}{4} L^{(t)}.
    \end{equation}
    %for some small \fixme{Miaoyan}{In what sense "small"? Add one sentence.} positive constants $C_4, C_5$. 
    Plugging the inequality~\eqref{eq:zeta_upper} into the decomposition~\eqref{eq:decomp2}, we obtain the contraction inequality 
    \begin{equation}\label{eq:decomp_t}
          L^{(t+1)} \leq \frac{3}{2} \xi  + \frac{1}{2} L^{(t)},
    \end{equation}
     where $\frac{1}{2}$ is the contraction parameter.

>>>>

    {\bf Step 3 (Derivation of contraction inequality).} In this step we derive the upper bound of $\zeta_{ib}$ and obtain the contraction inequality~\eqref{eq:proof_5_ineq}. Choose the constant $\tilde C$ in the condition SNR $\geq \tilde C p^{-K/2} \log p$ that satisfies the condition of Lemma~\ref{lem:upper_fgh}, inequalities~\eqref{eq:tilde_c1} and \eqref{eq:tilde_c2}. Note that 
    \begin{align}
        \zeta_{ib}^{(t)} &= \theta(i) \onormSize{}{ [ \mS_{ z(i):}  ]^s - [ \mS_{b:}  ]^s  }^2 \ind \offf{z^{(t+1)}(i) = b, \frac{1}{2}\onormSize{}{ [ \mS_{z(i):}  ]^s - [ \mS_{b:}  ]^s  }^2 \leq (\theta(i) m)^{-1} F_{ib}^{(t)} + G_{ib}^{(t)} + H_{ib}^{(t)} }\\
        & \leq \theta(i) \onormSize{}{ [ \mS_{ z(i):}  ]^s - [ \mS_{b:}  ]^s  }^2 \ind \offf{z^{(t+1)}(i) = b, \frac{1}{4}\onormSize{}{ [ \mS_{z(i):}  ]^s - [ \mS_{b:}  ]^s  }^2 \leq (\theta(i) m)^{-1} F_{ib}^{(t)} + G_{ib}^{(t)} } \\
        & \leq 64 \ind \offf{ z^{(t+1)}(i) = b} \of{  \frac{(F_{ib}^{(t)})^2}{ cm^2\onormSize{}{ [ \mS_{z(i):}  ]^s - [ \mS_{b:}  ]^s  }^2} + \frac{\theta(i)(G_{ib}^{(t)})^2}{ \onormSize{}{ [ \mS_{z(i):}  ]^s - [ \mS_{b:}  ]^s  }^2}    }
        %&\leq  \ind \offf{ z^{(t+1)}(i) = b} \of{  \frac{(F_{ib}^{(t)})^2}{ \onormSize{}{ [ \mS_{z(i):}  ]^s - [ \mS_{b:}  ]^s  }^2} + \frac{\theta(i)(G_{ib}^{(t)})^2}{ \onormSize{}{ [ \mS_{z(i):}  ]^s - [ \mS_{b:}  ]^s  }^2}    },\label{eq:zeta}
    \end{align}
    where the first inequality follows from the inequality~\eqref{eq:hib} in Lemma~\ref{lem:upper_fgh}, and the last inequality follows from the assumption that $\min_{i \in [p]} \theta(i) \geq c>0$. Following \citet[Step 4, Proof of Theorem 2]{han2020exact} and Lemma~\ref{lem:upper_fgh}, we have 
    \begin{align}\label{eq:f_sum}
          \frac{1}{p} \sum_{i \in [p]}\sum_{b \in [r]/z(i)} \ind \offf{ z^{(t+1)}(i) = b} \frac{(F_{ib}^{(t)})^2}{ cm^2 \onormSize{}{ [ \mS_{z(i):}  ]^s - [ \mS_{b:}  ]^s  }^2} \leq \frac{C_0 \bar C}{c m^2 \tilde C^2} L^{(t)},
    \end{align}
   for a positive universal constant $C$ and 
    \begin{align}
         \frac{1}{p} \sum_{i \in [p]}\sum_{b \in [r]/z(i)} \ind \offf{ z^{(t+1)}(i) = b} \frac{\theta(i)(G_{ib}^{(t)})^2}{ \onormSize{}{ [ \mS_{z(i):}  ]^s - [ \mS_{b:}  ]^s  }^2}  &\leq \frac{1}{512} \frac{1}{p} \sum_{i \in [p]}\theta(i) \sum_{b \in [r]/z(i)}   \ind \offf{ z^{(t+1)}(i) = b}  (\Delta_{\min}^2 + L^{(t)}) \\
         & \leq \frac{1}{512} (L^{(t+1)} + L^{(t)}), \label{eq:g_sum}
    \end{align}
    where the last inequality follows from the definition of $L^{(t)}$ and the constraint of $\mtheta$ in parameter space~\eqref{eq:family}. 
    %Choosing the constants $C, \bar C, C_2$ in~\eqref{eq:zeta}~\eqref{eq:f_sum}~\eqref{eq:g_sum} carefully \fixme{Miaoyan}{be specific. Add one sentence to explain}, 
   For $\tilde C$ also satisfies 
    \begin{equation}\label{eq:tilde_c3}
         \frac{C_0 \bar C}{c m^2 \tilde C^2} \leq \frac{1}{512},
    \end{equation}
    we have 
    \begin{equation}\label{eq:zeta_upper}
        \frac{1}{p}\sum_{i \in [p] }  \sum_{b \in [r]/z(i)}  \zeta_{ib}^{(t)} \leq  \frac{1}{8} L^{(t+1)}  + \frac{1}{4} L^{(t)}.
    \end{equation}
    %for some small \fixme{Miaoyan}{In what sense "small"? Add one sentence.} positive constants $C_4, C_5$. 
    Plugging the inequality~\eqref{eq:zeta_upper} into the decomposition~\eqref{eq:decomp2}, we obtain the contraction inequality 
    \begin{equation}\label{eq:decomp_t}
          L^{(t+1)} \leq \frac{3}{2} \xi  + \frac{1}{2} L^{(t)},
    \end{equation}
     where $\frac{1}{2}$ is the contraction parameter.
